---
title: "RP_Project_01"
author: "S. Heffron"
date: "Saturday, October 15, 2016"
output: html_document
---

# Reproducible Project - Project 1


```{r, echo=FALSE}
require(dplyr)
require(lubridate)
require(reshape2)
```

### Code for reading in the dataset and/or processing the data
```{r}
unzip("ActivityMonitorData.zip",exdir = "data")

AMD <- read.csv("data/activity.csv", stringsAsFactors=FALSE)
#### Convert date meta data from chr to date
AMD$date <- ymd(AMD$date)
```

#### Prepare objects for plot
```{r}
AMD_ETL_Date <- melt(AMD, id.vars="date", measure.vars="steps", na.rm=FALSE)
AMDFinalDate <- dcast(AMD_ETL_Date, date ~ variable, sum)
```

#### Histogram of the total number of steps taken each day
```{r, echo=FALSE}
plot(AMDFinalDate$date, AMDFinalDate$steps, type="h", main="Histogram of Daily Steps", xlab="Date", ylab="Steps per Day", col="blue", lwd=8)
```

#### Mean and median number of steps taken each day
```{r}
paste("Mean Steps per Day =", mean(AMDFinalDate$steps, na.rm=TRUE))
paste("Median Steps per Day =", median(AMDFinalDate$steps, na.rm=TRUE))
```

#### Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
AMD_Interval <- melt(AMD, id.vars="interval", measure.vars="steps", na.rm=TRUE)
```

#### Cast data frame to see mean steps per interval
```{r}
AMD_Int <- dcast(AMD_Interval, interval ~ variable, mean)
```

#### Plot line chart with average frequency of steps by interval and add line with mean
```{r, echo=FALSE}
plot(AMD_Int$interval, AMD_Int$steps, type="l", main="Frequency of Steps Taken at Each Interval", xlab="Interval ID", ylab="Steps", col="orange", lwd=2)
```


